New Metrics for Assessing Projection Pursuit Indexes, and Guiding Optimisation Choices

### 2024-09-15 jso.qmd
small fix in supplementary

The supplementary materials available at <https://github.com/huizezhang-sherry/paper-jso> include: 1) details of the indexes used in the simulation study, 2) the script to get started with using JSO in a PPGT and calculating smoothness and squintability, as explained in @sec-discussion, and the full code to reproduce the plots and summaries in this paper.

>>>>

The supplementary materials available at <https://github.com/huizezhang-sherry/paper-jso> include: 1) details of the indexes used in the simulation study, 2) the script to get started with using JSO in a PPGT and calculating smoothness and squintability, as explained in @sec-discussion, and (3) the full code to reproduce the plots and summaries in this paper.

### 2024-09-15 jso.tex
small fix in supplementary

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, opacitybacktitle=0.6, arc=.35mm, colback=white, title={Algorithm: Jellyfish Optimizer Pseudo Code}, titlerule=0mm, coltitle=black, bottomrule=.15mm, left=2mm, breakable, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, bottomtitle=1mm, opacityback=0, colframe=quarto-callout-note-color-frame, leftrule=.75mm]

@@

The supplementary materials available at
\url{https://github.com/huizezhang-sherry/paper-jso} include: 1) details
of the indexes used in the simulation study, 2) the script to get
started with using JSO in a PPGT and calculating smoothness and
squintability, as explained in Section~\ref{sec-discussion}, and the
full code to reproduce the plots and summaries in this paper.

>>>>

\begin{tcolorbox}[enhanced jigsaw, leftrule=.75mm, opacityback=0, toprule=.15mm, coltitle=black, opacitybacktitle=0.6, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, breakable, colback=white, toptitle=1mm, titlerule=0mm, left=2mm, arc=.35mm, bottomrule=.15mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}]

@@

The supplementary materials available at
\url{https://github.com/huizezhang-sherry/paper-jso} include: 1) details
of the indexes used in the simulation study, 2) the script to get
started with using JSO in a PPGT and calculating smoothness and
squintability, as explained in Section~\ref{sec-discussion}, and (3) the
full code to reproduce the plots and summaries in this paper.
